\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliographie}

\bibitem{spring-boot}
Spring Boot Documentation, VMware / Broadcom.
\url{https://docs.spring.io/spring-boot/docs/current/reference/html/} (consulté en 2026).

\bibitem{spring-security}
Spring Security Reference Documentation.
\url{https://docs.spring.io/spring-security/reference/} (consulté en 2026).

\bibitem{spring-data-jpa}
Spring Data JPA Documentation.
\url{https://docs.spring.io/spring-data/jpa/docs/current/reference/html/} (consulté en 2026).

\bibitem{thymeleaf}
Thymeleaf Documentation.
\url{https://www.thymeleaf.org/documentation.html} (consulté en 2026).

\bibitem{postgresql}
PostgreSQL Documentation, Version 18.
\url{https://www.postgresql.org/docs/} (consulté en 2026).

\bibitem{flyway}
Flyway Documentation, Redgate.
\url{https://documentation.red-gate.com/fd} (consulté en 2026).

\bibitem{bootstrap}
Bootstrap Documentation, Version 5.3.
\url{https://getbootstrap.com/docs/5.3/} (consulté en 2026).

\bibitem{openpdf}
OpenPDF — Libre PDF Library.
\url{https://github.com/LibrePDF/OpenPDF} (consulté en 2026).

\bibitem{uml}
OMG — Unified Modeling Language Specification.
\url{https://www.omg.org/spec/UML/} (consulté en 2026).

\bibitem{plantuml}
PlantUML — Open-source tool for UML diagrams.
\url{https://plantuml.com/} (consulté en 2026).

\bibitem{cahier}
Cahier des charges PFA — Système de gestion d'agence bancaire.
\texttt{documentation/cahier-charge-PFA.pdf}, projet \nomapplication.

\bibitem{gantt}
GanttProject — Project scheduling application.
\url{https://www.ganttproject.biz/} (consulté en 2026).

\end{thebibliography}
